Self-Supervised Learning of Generalized Policies in adversarial domains

### 2021-07-14 doc/paper/paper.tex
pygame init

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (CM) Atom[checkmate] [k=1]
  (SM) Atom[stalemate] [k=1]
  (QbK) Atom[white_queen_between_kings] [k=1]
  (KE) Atom[black_king_closed_in_edge_by_white_queen] [k=1]
  (KD) Dist[cell-has-white_king;adjacent_cell;cell-has-black_king] [k=4]
  (BKhA) Bool[And(cell-attaked-by-black_king,Not(cell-attaked-by-white))] [k=4]
  (A) Num[And(cell-attaked-by-black_king,Not(cell-attaked-by-white_queen))] [k=4]
  () Bool[And(row-has-white_queen,Exists(adjacent_row,row-has-black_king)))] [k=6]
  (WQadjBK_col) Bool[And(col-has-white_queen,Exists(adjacent_col,col-has-black_king)))] [k=6]
  (WQadjBK) Bool[And(cell-has-white_queen,Exists(adjacent_cell,cell-has-black_king)))] [k=6]
  (WQadjWK) Bool[And(cell-has-white_queen,Exists(adjacent_cell,cell-has-white_king)))] [k=6]
\end{Verbatim}

@@

\subsubsection{Feature Description}
$CM$. Checkmate\\
$SM$. Stalemate\\
$KE$. Black king is closed in an edge of the table by the white queen\\
$QbK$. White queen is somewhere between kings, rows or columns\\
$A$. The number of cells attaked by black king and not attacked by white queen\\
$BKhA$. Exist a cell attaked by Black king and no attacked by white pieces\\
$Qaw$. White queen is attaked and without protection, i.e. $WQadjBK AND WQadjWK$\\
$WQadjBK_line$. White queen is in an adjacent line to the black king, i.e. $WQadjBK_row OR WQadjWK_col$\\
$CA$. It is possible to decrease the number of cells attaked by black king and not attacked by white queen\\
$CCM$. It is possible to do checkmate in the current state

>>>>

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (CM) Atom[checkmate] [k=1]
  (SM) Atom[stalemate] [k=1]
  (QbK) Atom[white_queen_between_kings] [k=1]
  (KE) Atom[black_king_closed_in_edge_by_white_queen] [k=1]
  (KD) Dist[cell-has-white_king;adjacent_cell;cell-has-black_king] [k=4]
  (BKhA) Bool[And(cell-attaked-by-black_king,Not(cell-attaked-by-white))] [k=4]
  (A) Num[And(cell-attaked-by-black_king,Not(cell-attaked-by-white_queen))] [k=4]
  (WQadjBK_row) Bool[And(row-has-white_queen,Exists(adjacent_row,row-has-black_king)))] [k=6]
  (WQadjBK_col) Bool[And(col-has-white_queen,Exists(adjacent_col,col-has-black_king)))] [k=6]
  (WQadjBK) Bool[And(cell-has-white_queen,Exists(adjacent_cell,cell-has-black_king)))] [k=6]
  (WQadjWK) Bool[And(cell-has-white_queen,Exists(adjacent_cell,cell-has-white_king)))] [k=6]
\end{Verbatim}

@@

\subsubsection{Feature Description}
$CM$. Checkmate\\
$SM$. Stalemate\\
$KE$. Black king is closed in an edge of the table by the white queen\\
$QbK$. White queen is somewhere between kings, rows or columns\\
$A$. The number of cells attaked by black king and not attacked by white queen\\
$BKhA$. Exist a cell attaked by Black king and no attacked by white pieces\\
$Qaw$. White queen is attaked and without protection, i.e. $WQadjBK$ AND $WQadjWK$\\
$WQadjBK_line$. White queen is in an adjacent line to the black king, i.e. $WQadjBK_row$ OR $WQadjWK_col$\\
$CA$. It is possible to decrease the number of cells attaked by black king and not attacked by white queen\\
$CCM$. It is possible to do checkmate in the current state

\subsection{Checkmate in n with Rook}
\subsubsection{Description}

\subsubsection{Training instances}
\begin{Verbatim}[fontsize=\footnotesize]
  # .  k  .  .  K #
  # .  .  .  .  . #
  # .  .  .  .  . #
  # R  .  .  .  . #
  # .  .  .  .  . #
\end{Verbatim}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (CM) Atom[checkmate] [k=1]
  (SM) Atom[stalemate] [k=1]
  (QbK) Atom[white_rook_between_kings] [k=1]
  (KE) Atom[black_king_closed_in_edge_by_white_rook] [k=1]
  (KD) Dist[cell-has-white_king;adjacent_cell;cell-has-black_king] [k=4]
  (BKhA) Bool[And(cell-attaked-by-black_king,Not(cell-attaked-by-white))] [k=4]
  (A) Num[And(cell-attaked-by-black_king,Not(cell-attaked-by-white_rook))] [k=4]
  (WQadjBK_row) Bool[And(row-has-white_rook,Exists(adjacent_row,row-has-black_king)))] [k=6]
  (WQadjBK_col) Bool[And(col-has-white_rook,Exists(adjacent_col,col-has-black_king)))] [k=6]
  (WQadjBK) Bool[And(cell-has-white_rook,Exists(adjacent_cell,cell-has-black_king)))] [k=6]
  (WQadjWK) Bool[And(cell-has-white_rook,Exists(adjacent_cell,cell-has-white_king)))] [k=6]
\end{Verbatim}

\subsubsection{Feature Description}
$CM$. Checkmate\\
$SM$. Stalemate\\
$KE$. Black king is closed in an edge of the table by the white queen\\
$QbK$. White queen is somewhere between kings, rows or columns\\
$A$. The number of cells attaked by black king and not attacked by white queen\\
$BKhA$. Exist a cell attaked by Black king and no attacked by white pieces\\
$Qaw$. White queen is attaked and without protection, i.e. $WQadjBK$ AND $WQadjWK$\\
$WQadjBK_line$. White queen is in an adjacent line to the black king, i.e. $WQadjBK_row$ OR $WQadjWK_col$\\
$CA$. It is possible to decrease the number of cells attaked by black king and not attacked by white queen\\
$CCM$. It is possible to do checkmate in the current state
